### 2017-05-02 paper/paper.tex
final paper tweaks

\quad Sparse binary data of this kind quickly becomes unwieldy as traditional distance measures are highly prone to error. Such measures include k-means, PCA analysis (for dimensionality reduction), DBSCAN, and agglomerative clustering. Typically, the computational cost is prohibitive (Plumley, (2002)) or the numerical values are highly unstable during computation. The goal in our application is to reduce the effective categorical space and classify the businesses into a narrower subset?on the order of ~50. Not surprisingly, this scenario is almost identical to that encountered when processing and analyzing large corpuses of text. Almost every form of textual representation falls into the ?bag-of-words? paradigm where vectors are used to represent each document, and each element corresponds to either the frequency of a given term in the dictionary (i.e., all words from all documents) or the binary existence of the word in the document. Since each document is highly unlikely to have an instance of all terms, the combination of these vectors results in a very large, very sparse matrix of n documents by p terms.

>>>>

\quad Sparse binary data of this kind quickly becomes unwieldy as traditional distance measures are highly prone to error. Such measures include k-means, PCA analysis (for dimensionality reduction), DBSCAN, and agglomerative clustering. Typically, the computational cost is prohibitive [8] or the numerical values are highly unstable during computation. The goal in our application is to reduce the effective categorical space and classify the businesses into a narrower subset\--on the order of 50. Not surprisingly, this scenario is almost identical to that encountered when processing and analyzing large corpuses of text. Almost every form of textual representation falls into the ?bag-of-words? paradigm where vectors are used to represent each document, and each element corresponds to either the frequency of a given term in the dictionary (i.e., all words from all documents) or the binary existence of the word in the document. Since each document is highly unlikely to have an instance of all terms, the combination of these vectors results in a very large, very sparse matrix of n documents by p terms.
